Basic Model formulation

### 2015-02-26 documentation/model_formulation.Rmd
update model formulation

Mechanistic explanations can be the limitations by a globally diffuse resource, like water, or the occupation of space and the subsequent limitation of photosynthetic active surface.

@@

$$ c_11 = q_{1|1}/\rho_1 = \frac{\rho_11}{\rho_1^2}$$

@@

@@

The following shows bifurcation diagrams over an environmental gradient.

@@

@@

plot(rho_1 ~ b, data = cbind(output, iterations), type = "p", pch  = 20, ylim = c(0,1))

The following shows bifurcation diagrams over a livestock density gradient.

@@

plot(rho_1 ~ L, data = cbind(output, iterations), type = "p", pch  = 20, ylim = c(0,1))

>>>>

Mechanistic explanations can be the limitations by a globally diffuse resource, like water. 
(We do not discuss the occupation of space as a global resource and the subsequent limitation of photosynthetic active surface, since this is implemented by adding explicit space to the model.)

@@

$$ c_{11} = q_{1|1}/\rho_1 = \frac{\rho_{11}}{\rho_1^2}$$

@@

**apparently this solution is wrong!! Instead, I draw  initial $rho_11$ values systematically and elimitate those that produce invalid $m_ini$**

This works quite well, but produces unequal distributions of arrows along the y-axis.

@@

The following shows bifurcation diagrams over an environmental gradient, $b$, as well as over a gradient of livestock density, $L$.

```{r, echo=FALSE, fig.height = 3}

@@

par(mfrow= c(1,2), bty = "n", mar = c(4,4,1,0))

@@

plot(rho_1 ~ b, data = cbind(output, iterations), type = "p", pch  = 20, ylim = c(0,1), cex = 0.5)

@@

plot(rho_1 ~ L, data = cbind(output, iterations), type = "p", pch  = 20, ylim = c(0,1), cex = 0.5)
